The NEOCP in the Era of LSST

### 2022-05-15 paper/paper.tex
start writing the methods

\documentclass[twocolumn, twocolappendix]{aastex631}
\received{\today}
\shorttitle{Detecting DCOs with LISA}
\graphicspath{{../figures/}}

@@

\newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}

@@

% affiliations
\newcommand{\cfa}{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
\newcommand{\mpa}{Max-Planck-Institut für Astrophysik, Karl-Schwarzschild-Straße 1, 85741 Garching, Germany}
\newcommand{\cca}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
\newcommand{\UvA}{Anton Pannekoek Institute for Astronomy \& Grappa, University of Amsterdam, Postbus 94249, 1090 GE Amsterdam, The Netherlands}
\newcommand{\UW}{Department of Astronomy, University of Washington, Seattle, WA, 98195}

@@

@@

\keywords{gravitational waves, gravitational wave detectors, compact objects, stellar mass black holes, neutron stars, binary stars, stellar evolution, pulsars}

@@

\begin{acknowledgements}
    We'll thank some people here
\end{acknowledgements}

\software{}

>>>>

\documentclass[twocolumn, twocolappendix]{aastex631}
\received{\today}
\shorttitle{NEOCP in LSST era}
\graphicspath{{figures/}}

@@

\newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}
\newcommand{\dig}{\texttt{digest2}}

@@

% affiliations
\newcommand{\UW}{Department of Astronomy, University of Washington, Seattle, WA, 98195}

@@

\author[0000-0003-1996-9252]{M. Juric}
\affiliation{\UW}

\author{\dots more}

@@

\keywords{Near-Earth objects, Asteroids, Solar system, Small Solar System bodies, Surveys}

@@

\begin{acknowledgements}
    Acknowledgements
\end{acknowledgements}

\software{\texttt{astroML} \citep{VanderPlas+2012,VanderPlas+2014}, \texttt{scipy} \citep{Virtanen+2020}}
